Reproducibility in plant pathology: where do we stand and a way forward

### 2021-07-27 analysis/paper/paper.Rmd
Acknowledge David in paper
Add visualisation references to Rmd file

The statistical analysis was performed using R version 4.1.0 [@RCT2021] on an Apple MacBook Air (M1, 2020).
Bayesian mixed-effect models were fit using the contributed package 'brms' [@Burkner2018] to evaluate the fixed effects of the publication (journal title), article class, molecular focus, five-year journal impact factor, journal open access policy on the reproducibility index and year to test for changes over time in the reproducibility index.

@@

Model finesses were evaluated using model summaries and diagnostic plots from 'brms' [@Burkner2018] and posterior fits using `pp_check()` from the contributed R package 'bayesplot' [@Gabry2019].

Probability of direction or maximum probability of effect was plotted, `pd()`, and a test for practical equivalence, `equivalence_test()`, was performed for each model using the contributed R package 'bayestestR' [@Makowski2019].

@@

>>>>

The statistical analysis was performed using R version 4.1.0 [@RCT2021] on an Apple MacBook Air (M1, 2020).
Bayesian mixed-effect models were fit using the contributed package 'brms' (version 2.15.0) [@Burkner2018] to evaluate the fixed effects of the publication (journal title), article class, molecular focus, five-year journal impact factor, journal open access policy on the reproducibility index and year to test for changes over time in the reproducibility index.

@@

Model finesses were evaluated using model summaries and diagnostic plots from 'brms' (version 2.15.0) [@Burkner2018] and posterior fits using `pp_check()` from the contributed R package 'bayesplot' (version 1.8.1) [@Gabry2019].

Probability of direction or maximum probability of effect was plotted, `pd()`, and a test for practical equivalence, `equivalence_test()`, was performed for each model using the contributed R package 'bayestestR' (version 0.10.0) [@Makowski2019].

Data were visualised using 'ggplot2' (version 3.3.5) [@Wickham2016], 'ggpubr' (version 0.4.0) [@Kassambara2020] and patchwork (version 1.1.1) [@Pedersen2020].

@@

The authors are grateful for insightful comments from Dr. David Ferris on the final manuscript.
